---
title: '21-10-2019 Meeting'
author: "*Compiled on `r date()` by `r Sys.info()['user']`*"
output: 
  html_document:
    toc: true
    toc_float: yes
    number_sections: true
    theme: cerulean
    highlight: haddock
    includes: 
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
library(tidyverse)
library(survival)
library(AlgDesign)
library(DT)
library(stargazer)
library(xtable)
```


```{r, include = FALSE}
master_surv_resp <- read_csv("master_survey_resp.csv")
version_to_package <- read_csv("version_to_package.csv")
packages <- read_csv("packages.csv")


version1<-version_to_package %>% 
  filter(package<=16) %>% 
  left_join(packages)

survey_ce1<-master_surv_resp %>% 
  select(survey_id, survey_version, choice) %>% 
  mutate(RES = ifelse(choice == 1, 1, 0)) %>% 
  merge(version1, all = TRUE) %>% 
  arrange(survey_id) %>% 
  mutate(STR=c(1:205)) 

version2<-version_to_package %>% 
  filter(package>=17)%>% 
  left_join(packages)

survey_ce2<-master_surv_resp %>% 
  select(survey_id, survey_version, choice) %>% 
  mutate(RES = ifelse(choice == 2, 1, 0)) %>% 
  merge(version2, all = TRUE)%>% 
  arrange(survey_id) %>% 
  mutate(STR=c(1:205)) 

survey_ce_total <- rbind(survey_ce1, survey_ce2)

survey_ce <- survey_ce_total %>% 
  mutate(ASC=1) %>% 
  select(STR,RES, ASC, 6:8) %>% 
  mutate(STR=STR*1000+1) %>% 
  arrange(STR) %>%
  mutate(sos = as.factor(sos), info = as.factor(info), own = as.factor(own)) # this fixes problem i think? 
  
```
## Package Key

Package |	Info | Own |	SOS
-----	|----- | ----- | -----
1 |	Non-anonymous |	Industry |	No
2 |	Non-anonymous |	Government |	Yes
3	 | Non-anonymous |	Fishers |	No
4 |	Anonymous |	Public Access	| Yes
5 |	Anonymous |	Public Access |	No
6 |	Anonymous |	Government |	No
7 |	Anonymous |	Fishers |	Yes
8 |	Non-anonymous |	Public Access |	No
9 |	Anonymous |	Government |	Yes
10 | 	Anonymous |	Industry |	No
11 |	Non-anonymous |	Public Access |	Yes
12 |	Non-anonymous |	Fishers |	Yes
13 |	Non-anonymous |	Industry |	Yes
14 |	Anonymous |	Industry |	Yes
15 |	Anonymous |	Fishers |	No
16 |	Non-anonymous |	Government |	No

```{r, include = FALSE}
library(survival)

clogout1<-clogit(RES~sos+info+own+strata(STR), data=survey_ce)
clogout1
summary(clogout1)

# sos	1 = no, 2 = yes
# info 	1 = non, 2 = anon
# own	1 = fishers, 2 = industry, 3 = govt, 4 = public access
#adopt : 1 = accept, 0 = decline
```

## Phase 1 model results
```{r stargazer1, results = 'asis', include = FALSE}
#adoption_1 <- stargazer(clogout1, title = "Phase 1 Conditional Logit Model", type = "html")
```

```{r, echo = FALSE}
summary(clogout1)
```

```{r, include = FALSE}
pt2_response<-master_surv_resp %>% 
  select(survey_id, package_nopackage)

pt2_join<-survey_ce_total %>% 
  filter(RES==1) %>% 
  mutate(STR=STR*1000+2) %>% 
  select(STR, sos,info,own,survey_version,package, survey_id) %>% 
  left_join(pt2_response) %>%
  mutate(RES=package_nopackage) %>% 
  select(-package_nopackage)
  
  
pt2_package<-pt2_join %>% 
  mutate(ASC=1)
  
pt2_nopackage<-pt2_join %>% 
  mutate(sos=0, info=0, own=0, ASC=0) %>% 
  mutate(RES = ifelse(RES == 1, 0, 1))

survey_ce_pt2_total<-rbind(pt2_package, pt2_nopackage)

survey_ce_pt2<-survey_ce_pt2_total %>% 
  select(STR,RES, ASC, sos,info,own) %>% 
  arrange(STR) %>%
  mutate(sos = as.factor(sos), info = as.factor(info), own = as.factor(own))

ce_total<-rbind(survey_ce, survey_ce_pt2) 

```

```{r, include = FALSE}
clogout2<-clogit(RES~ASC+sos+info+own+strata(STR), data=ce_total)
clogout2
summary(clogout2)
```

## Phase 2 model results
```{r stargazer2, results = "asis", include = FALSE}
#adoption_2 <- stargazer(clogout2, title = "Phase 2 Conditional Logit Model", type = "html")
```

```{r, echo = FALSE}
summary(clogout2)
```


```{r, include = FALSE}
library(AlgDesign)
ffd <- gen.factorial(c(2,2,4), varNames = c("sos", "info", "own"), factors = "all") # construct a full factorial design which has two 2 level attributes and one 4 level attribute. factors = "all" indicates that all arguments are factors
ffd 

all_packages <- ffd %>%
  mutate(STR = 1001, package = 1:16) #RES = rep(c(1,0),8))

level_probs1 <- predict(clogout1, newdata = all_packages, type = "risk", se.fit = TRUE)

graph_data1 <- data.frame(all_packages, level_probs1)  

#reasoning for predicting out a clogit model:
#https://markmail.org/search/?q=list%3Aorg.r-project.r-help+predict+clogit#query:list%3Aorg.r-project.r-help%20predict%20clogit%20from%3A%22Therneau%2C%20Terry%20M.%2C%20Ph.D.%22+page:1+mid:tsbl3cbnxywkafv6+state:results
#https://stackoverflow.com/questions/35329585/how-to-get-fitted-values-from-clogit-model

# sos	1 = no, 2 = yes
# info 	1 = non, 2 = anon
# own	1 = fishers, 2 = industry, 3 = govt, 4 = public access
#adopt : 1 = accept, 0 = decline

graph_data11 <- graph_data1 %>%
  mutate(level_probs1 = fit/(fit+ 1),
         level_se = se.fit/(se.fit + 1)) %>%
  select(-fit, -se.fit, -STR) %>%
  arrange(-level_probs1) %>%
  select(package, info, own, sos, level_probs1, level_se) %>%
  mutate(info = case_when(
    info == 1 ~ "Non-anon",
    info == 2 ~ "Anon"
  ), 
  own = case_when(
   own == 1 ~ "Fishers",
   own == 2 ~ "Industry", 
   own == 3 ~ "Government", 
   own == 4 ~ "Public Access"
  ),
  sos = case_when(
    sos == 1 ~ "No",
    sos == 2 ~ "Yes"
  ))
```

## Phase 1 clogit model probability results for each package

```{r, echo = FALSE}
DT::datatable(graph_data11)

```

## Phase 1 conditional logit model probability of adoption exploration
```{r, echo = FALSE}
ggplot( data = graph_data11) +
  #geom_line(aes(color = Sex)) +
  geom_line(aes(x = sos, y = level_probs1)) +
  #geom_line(aes(x = info, y = level_probs1)) +
  #geom_line(aes(x = own, y = level_probs1)) +
  #geom_ribbon(aes(ymin = level_probs1 - level_se, ymax = level_probs1 + level_se, fill = info), alpha = 0.3) +
  theme_bw() +
  scale_x_discrete(expand = c(0,1)) +
  labs(x = "SOS Capability", y = "Predicted probability of adoption", title = "Phase 1")

ggplot( data = graph_data11) +
  #geom_line(aes(color = Sex)) +
  #geom_line(aes(x = sos, y = level_probs1)) +
  geom_line(aes(x = info, y = level_probs1)) +
  #geom_line(aes(x = own, y = level_probs1)) +
  #geom_ribbon(aes(ymin = level_probs1 - level_se, ymax = level_probs1 + level_se, fill = info), alpha = 0.3) +
  theme_bw() +
  scale_x_discrete(expand = c(0,1)) +
  labs(x = "Information Access", y = "Predicted probability of adoption", title = "Phase 1")

ggplot( data = graph_data11) +
  #geom_line(aes(color = Sex)) +
  #geom_line(aes(x = sos, y = level_probs1)) +
  #geom_line(aes(x = info, y = level_probs1)) +
  geom_line(aes(x = own, y = level_probs1)) +
  #geom_ribbon(aes(ymin = level_probs1 - level_se, ymax = level_probs1 + level_se, fill = info), alpha = 0.3) +
  theme_bw() +
  scale_x_discrete(expand = c(0,1)) +
  labs(x = "Ownership of data", y = "Predicted probability of adoption", title = "Phase 1")

```


```{r, include = FALSE}
ffd <- gen.factorial(c(2,2,4), varNames = c("sos", "info", "own"), factors = "all") # construct a full factorial design which has two 2 level attributes and one 4 level attribute. factors = "all" indicates that all arguments are factors
ffd 

all_packages <- ffd %>%
  mutate(STR = 1001, ASC = 1, package = 1:16) #RES = rep(c(1,0),8))

level_probs2 <- predict(clogout2, newdata = all_packages, type = "risk", se.fit = TRUE)

graph_data2 <- data.frame(all_packages, level_probs2)  

#reasoning for predicting out a clogit model:
#https://markmail.org/search/?q=list%3Aorg.r-project.r-help+predict+clogit#query:list%3Aorg.r-project.r-help%20predict%20clogit%20from%3A%22Therneau%2C%20Terry%20M.%2C%20Ph.D.%22+page:1+mid:tsbl3cbnxywkafv6+state:results
#https://stackoverflow.com/questions/35329585/how-to-get-fitted-values-from-clogit-model

graph_data22 <- graph_data2 %>%
  mutate(level_probs2 = fit/(fit+ 1),
         level_se = se.fit/(se.fit + 1)) %>%
  select(-fit, -se.fit, -STR) %>%
  select(package, sos, info, own, level_probs2, level_se) %>%
  arrange(desc(level_probs2)) %>%
  mutate(info = case_when(
    info == 1 ~ "Non-anon",
    info == 2 ~ "Anon"
  ), 
  own = case_when(
   own == 1 ~ "Fishers",
   own == 2 ~ "Industry", 
   own == 3 ~ "Government", 
   own == 4 ~ "Public Access"
  ),
  sos = case_when(
    sos == 1 ~ "No",
    sos == 2 ~ "Yes"
  )) 
```

## Phase 2 clogit model probability results for each package
```{r, echo = FALSE}
DT::datatable(graph_data22)
```

## Phase 2 conditional logit model probability of adoption exploration
```{r, echo = FALSE}
ggplot( data = graph_data22) +
  #geom_line(aes(color = Sex)) +
  geom_line(aes(x = sos, y = level_probs2)) +
  #geom_line(aes(x = info, y = level_probs1)) +
  #geom_line(aes(x = own, y = level_probs1)) +
  #geom_ribbon(aes(ymin = level_probs1 - level_se, ymax = level_probs1 + level_se, fill = info), alpha = 0.3) +
  theme_bw() +
  scale_x_discrete(expand = c(0,1)) +
  labs(x = "SOS Capability", y = "Predicted probability of adoption", title = "Phase 2")

ggplot( data = graph_data22) +
  #geom_line(aes(color = Sex)) +
  #geom_line(aes(x = sos, y = level_probs1)) +
  geom_line(aes(x = info, y = level_probs2)) +
  #geom_line(aes(x = own, y = level_probs1)) +
  #geom_ribbon(aes(ymin = level_probs1 - level_se, ymax = level_probs1 + level_se, fill = info), alpha = 0.3) +
  theme_bw() +
  scale_x_discrete(expand = c(0,1)) +
  labs(x = "Information Access", y = "Predicted probability of adoption", title = "Phase 2")

ggplot( data = graph_data22) +
  #geom_line(aes(color = Sex)) +
  #geom_line(aes(x = sos, y = level_probs1)) +
  #geom_line(aes(x = info, y = level_probs1)) +
  geom_line(aes(x = own, y = level_probs2)) +
  #geom_ribbon(aes(ymin = level_probs1 - level_se, ymax = level_probs1 + level_se, fill = info), alpha = 0.3) +
  theme_bw() +
  scale_x_discrete(expand = c(0,1)) +
  labs(x = "Ownership of data", y = "Predicted probability of adoption", title = "Phase 2")
```

## Willingness to Pay/Recieve
```{r, include = FALSE}
master_surv_resp <- read_csv("master_survey_resp.csv")
version_to_package <- read_csv("version_to_package.csv")
packages <- read_csv("packages.csv")
```

```{r, include = FALSE}
pt2_response<-master_surv_resp %>% 
  select(survey_id, country, package_nopackage,  wtp_1, wtp_2, wtp_3, wtp_4, wtr_1, wtr_2, wtr_3, wtr_4)

pt2_join_wtp <-survey_ce_total %>% 
  filter(RES==1) %>% 
  mutate(STR=STR*1000+2) %>% 
  select(survey_id, package, sos,info,own) %>% 
  left_join(pt2_response) %>%
  mutate(RES=package_nopackage) %>% 
  filter(RES == 1) %>%
  select(-RES, -package_nopackage, -wtr_1, -wtr_2, -wtr_3, -wtr_4) %>%
  mutate(wtp_1 = ifelse(!is.na(wtp_1), 5, NA),
        wtp_2 = ifelse(!is.na(wtp_2), 10, NA),
        wtp_3 = ifelse(!is.na(wtp_3), 15, NA), 
        wtp_4 = ifelse(!is.na(wtp_4), 20, NA)) %>%
  mutate(wtp = case_when(
    !is.na(wtp_4) ~ wtp_4,
    is.na(wtp_4) & !is.na(wtp_3) ~ wtp_3, 
    is.na(wtp_4) & is.na(wtp_3) & !is.na(wtp_2) ~ wtp_2,
    is.na(wtp_4) & is.na(wtp_3) & is.na(wtp_2) & !is.na(wtp_1) ~ wtp_1)
    ) %>%
  select(survey_id, country, package, wtp)

  

pt2_join_wtr <-survey_ce_total %>% 
  filter(RES==1) %>% 
  mutate(STR=STR*1000+2) %>% 
  select(survey_id, package, sos,info,own) %>% 
  left_join(pt2_response) %>%
  mutate(RES=package_nopackage) %>% 
  filter(RES == 0) %>%
  select(-RES, -package_nopackage, -wtp_4, -7, -8, -9) %>%
  mutate(wtr_1 = ifelse(!is.na(wtr_1), 5, NA),
        wtr_2 = ifelse(!is.na(wtr_2), 10, NA),
        wtr_3 = ifelse(!is.na(wtr_3), 15, NA), 
        wtr_4 = ifelse(!is.na(wtr_4), 20, NA)) %>%
  mutate(wtr = case_when(
    !is.na(wtr_4) ~ wtr_4,
    is.na(wtr_4) & !is.na(wtr_3) ~ wtr_3, 
    is.na(wtr_4) & is.na(wtr_3) & !is.na(wtr_2) ~ wtr_2,
    is.na(wtr_4) & is.na(wtr_3) & is.na(wtr_2) & !is.na(wtr_1) ~ wtr_1)
    ) %>%
  select(survey_id, country, package, wtr)
  
wtp_wtr <- full_join(pt2_join_wtp, pt2_join_wtr) %>%
  mutate(wtr = wtr*-1) 

wtp_wtr_1 <- wtp_wtr %>%
  filter(package < 17)

wtp_wtr_2 <- wtp_wtr %>%
  filter(package>16) %>%
  left_join(version_to_package) %>%
  mutate(package =  survey_version) %>%
  select(-survey_version)

wtp_wtr_final <- full_join(wtp_wtr_1, wtp_wtr_2)

wtp_wtr_final_1 <- wtp_wtr_final %>%
  mutate(money = ifelse(is.na(wtp), wtr, wtp)) %>%
  select(-wtr, -wtp)
```

```{r, warning = FALSE}
ggplot(data = wtp_wtr_final_1, aes(x = as.factor(package), y = money)) +
  geom_jitter() +
  theme_bw() +
  facet_wrap(~country) 
```



