---
title: "BR GFW Report 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(plotly)
library(ggplot2)
library(ggpubr)
library(reshape2)
```

Reading in the survey, filtering only for Mexico
```{r, include=FALSE}
survey <- read_csv("master_survey_resp.csv")

head(survey)
```
#4. Gear
```{r}
#Changing wide to long form for gear

gear<- survey %>% 
  select(8,11:17) %>% 
  gather(gear, use, -country) %>% 
  filter(use==1) %>% 
  ggplot(aes(x=gear, fill=country))+
  geom_bar()+
  geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5), color = "white")+
  theme_pubclean()

gear
```
#5. Boat Ownership
```{r}
ggplot(survey, aes(x=boat_status, fill=country))+
  geom_bar()+
  geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5), color = "white")+
  theme_pubclean()
```
#6.
##a. Boat Length
```{r}
ggplot(survey, aes(x=boat_length_m, fill=country))+geom_histogram()
```
##b. Material
```{r}
ggplot(survey, aes(x=boat_material, fill=country))+
  geom_bar()+
  geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5), color = "white")+
  theme_pubclean()
```

##c. Is the boat motorized
```{r}
ggplot(survey, aes(x=boat_motorized, fill=country))+
  geom_bar()+
  geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5), color = "white")+
  theme_pubclean()
```

##d. Is there an onboard power/ electricity source?

```{r}
ggplot(survey, aes(x=boat_power, fill=country))+
  geom_bar()+
  geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5), color = "white")+
  theme_pubclean()
```

#7. Please check all the types of technology that you use at least once a week, if any
```{r}
#Changing wide to long form for gear

tech<- survey %>% 
  select(8,25:29) %>% 
  gather(tech, use, -country) %>% 
  filter(use==1) %>% 
  ggplot(aes(x=tech, fill=country))+
  geom_bar()+
   geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5), color = "white")+
  theme_pubclean()

tech
```

#8. Please check all the types of technology that you use or have used at some point for your fishing activity
```{r}
#Changing wide to long form for gear

fish_tech<- survey %>% 
  select(8,31:38) %>% 
  gather(fish_tech, use, -country) %>% 
  filter(use==1) %>% 
  ggplot(aes(x=fish_tech, fill=country))+
  geom_bar()+
   geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5), color = "white")+
  theme_pubclean()

fish_tech
```

#9. What type of tracking technology did you use on your vessel?
```{r}
table(survey$text_vms)
```

#20. Combining all seasons, what are your top three targeted fisheries?
```{r}
target_sp<- survey %>% 
  select(8,67:69) %>% 
  gather(target, sp, -country)

#counts table
target_tb<-target_sp %>% 
  group_by(target, sp) %>% 
  count()

target_tb

#bar plot
ggplot(target_sp, aes(x=sp, fill=target))+
  geom_bar()+
   geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5), color = "white")+
  theme_pubclean()


```

#21. What percent of the total catch (out of 100%) goes to...	
  a. Own/household consumption
	b. Shared to neighboring household
	c. Traded in local market
	d. Export
	e. Other
```{r}
#a. Own/household consumption
ggplot(survey, aes(x=fraction_personal, fill=country))+geom_histogram()

#b. Shared to neighboring household
ggplot(survey, aes(x=fraction_neighbor, fill=country))+geom_histogram()

#c. Traded in local market
ggplot(survey, aes(x=fraction_local_trade, fill=country))+geom_histogram()

#d. Export
ggplot(survey, aes(x=fraction_export, fill=country))+geom_histogram()

#e. Other
ggplot(survey, aes(x=fraction_other, fill=country))+geom_histogram()

```
21.x Other	
```{r}
unique(survey$other_fraction)
```

22. Are you part of a fishing organization?	
```{r}
ggplot(survey, aes(x=fishing_organization, fill=country))+
  geom_bar()+
  geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5))+
  theme_pubclean()
```

23. What type of organization?
```{r}
ggplot(survey, aes(x=fishing_organization, fill=country))+
  geom_bar()+
  geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5))+
  theme_pubclean()
```
Other	


24. What role do you have in the organization?	
```{r}
ggplot(survey, aes(x=fishing_organization, fill=country))+
  geom_bar()+
  geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5))+
  theme_pubclean()
```
Other	
25. How many members does the organization have?
```{r}
ggplot(survey, aes(x=factor(1), y=fishing_org_members))+
  geom_jitter(aes(color=country))+
  labs(x=NULL)
```

26. Who is allowed to fish for your #1 targeted fishery, ${target_species_one} ?	
```{r}
ggplot(survey, aes(x=access_target_species, fill=country))+
  geom_bar()+
  geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5), color="white")+
  theme_pubclean()
```
Other	

#27. Please indicate what restrictions exist for your #1 targeted fisherie, ${target_species_one}.	
```{r}
restrictions<- survey %>% 
  select(8,84:90) %>% 
  gather(regulations, n, -country) %>% 
  filter(n==1) %>% 
  ggplot(aes(x=restrictions, fill=country))+
  geom_bar()+
  geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5), color = "white")+
  theme_pubclean()

restrictions
```
Other	

#28. Who is responsible for enforcement in your community?	
```{r}
enforcement<- survey %>% 
  select(8,92:98) %>% 
  gather(enforcement, n, -country) %>% 
  filter(n==1) %>% 
  ggplot(aes(x=enforcement, fill=country))+
  geom_bar()+
  geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5), color = "white")+
  theme_pubclean()

enforcement
```
Other	

#29. On average, how often are fishing regulations enforced?	
```{r}
ggplot(survey, aes(x=enforcement_interval, fill=country))+
  geom_bar()+
  geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5), color="white")+
  theme_pubclean()
```
Other	

#30. How severe is the punishment when a person gets caught violating the fishing regulations?	
```{r}
ggplot(survey, aes(x=punishment_severity, fill=country))+
  geom_bar()+
  geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5), color="white")+
  theme_pubclean()
```

#31. Are there any closed areas in your fishing area?	
```{r}
ggplot(survey, aes(x=mpa, fill=country))+
  geom_bar()+
  geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5), color="white")+
  theme_pubclean()
```
#32. Wat do you think are the biggest problems your fishery faces?	
  1.
	2.
	3.


#33. How do you think the problems you mentioned can be solved?	
  1.
	2.
	3.

34. Please rank the following problems from 1 to 4, where 1 has the strongest impact on your fishing activity and 4 has the least impact on your fishing activity	
  Rank 1.
	Rank 2.
	Rank 3.
	Rank 4.
	
```{r}
rank<- survey %>% 
  select(110:113) %>% 
  gather(rank, problem) %>% 
  group_by(problem) %>% 
  na.omit() %>%
  ggplot(aes(x=problem))+
  geom_bar(aes(fill=rank), position=position_dodge(0.8), width=0.8)+
  theme_pubclean()

rank
```



35. In the last few years, the current fish catch has…
```{r}
trend<- survey %>% 
  select(8, 114) %>% 
  na.omit() %>%
  ggplot(aes(x=catch_trends, fill=country))+
  geom_bar()+
    geom_text(stat = 'count', aes(label = ..count..), position = position_stack(vjust = .5), color="white")+
  theme_pubclean()

trend
```
36. How much do you agree with the following statements	a. Formal stock assessments help to sustainably manage fisheries
	b. I have many options if I decide to no longer be a fisher
	c. In general, the fisheries in this region are doing well
	d. I am worried about the future of our fishery resources
	e. Outside small-scale fishers are always entering our fishing grounds/concession
	f. Outside industrial fishers are always entering our fishing grounds/concession
	g. Everyone in the fishing community knows where other fishers go (there are no secret spots)
	h. In general, my fishing activity implies severe risks to my life
	i. I feel I have a voice in how my fishing area is managed
37. Please indicate how much you trust the following groups	a. Other members in my fishing community
	b. Other fishing communities in the region
	c. Fishing association leaders
	d. Fisheries officers
	e. Police or security that might enforce poaching events
	f. Consultants that conduct assessments with fishing associations
	g. Fishery scientists
	h. Local conservation groups
	i. Non-Governmental Organizations
	j. National Government
	k. Local Government
	l. Private Companies
38. Please indicate how satisfied you were when working with the following organizations	a. Non-Governmental Organizations
	b. Private Companies
	c. Government Organizations
39. What is your age?	
40. How many years have you been fishing?	
41.What is your level of education? (Please choose one)	
Other	
42. What is your average monthly income?	
43. What percent (out of 100%) of your annual income comes from fishing?	
44. What percent (out of 100%) of your income is spent on expenses related to fishing?	
